### 2022-09-02 README.Rmd
LMA typo

-   Trips dataset with Origin and Destination, at *Freguesia* level, disaggregated by transport mode, from @IMOB  
-   [CAOP 2020](https://www.dgterritorio.gov.pt/cartografia/cartografia-tematica/caop?language=en) - Official limits of Portuguese areas.
-   Road network from [OpenStreetMap](https://www.openstreetmap.org/#map=11/38.7053/-9.1585)  
-   Main public transport interfaces at Lisbon Metro Region, provided by [Transportes Metropolitanos de Lisboa](https://www.tmlmobilidade.pt/)

>>>>

-   Trips dataset with Origin and Destination, at *Freguesia* level, disaggregated by transport mode, from @IMOB  
-   [CAOP 2020](https://www.dgterritorio.gov.pt/cartografia/cartografia-tematica/caop?language=en) - Official limits of Portuguese areas.
-   Road network from [OpenStreetMap](https://www.openstreetmap.org/#map=11/38.7053/-9.1585)  
-   Main public transport interfaces at Lisbon Metropolitan Area, provided by [Transportes Metropolitanos de Lisboa](https://www.tmlmobilidade.pt/)
